Contracts for Contracts

### 2022-12-13 paper.tex
intro

>>>>

At the concetual level, behavioral contracts is complementary to smart
contracts, in this sense that they are both agreement -- between software
components for the former, and between transactional parties for the later.
Thus, the two ``contracts'' indeed mean the same thing but just different levels
of enforcement.
